Proportional multi-state multiple-cohort life table model

### 2018-04-18 MSLT/MSLTdoc.Rmd
loop spline

```{r, echo=TRUE}
##Example for Greater London. First, extract rates of interest and add to GBD_population frame (change the name of the data frame).
##COULD USE A FUNCTION AND ALOOP AS WITH THE GRAPHS TO GENERATE DATA FOR EACH OF THE DISEASE FOR DISMOD.
##Create dataframe with mortality data males for Greater London (test spline, then need to better organise the row data from GBD)
##I used spline function as the rates are not always monotonic.

##Mortality rates

Mortality_males <- filter(GBDGL, measure == "deaths", sex == "male", cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate)

x=Mortality_males$age_cat
y=log(Mortality_males$one_rate)
plot(x,y)
Mortality_males_interpolated <- as.data.frame(spline(x, y, n = 5 *length (x), xmin = min(x-2), xmax = max(x + 2)))
Mortality_males_interpolated$y <- exp(Mortality_males_interpolated$y)
plot(Mortality_males_interpolated$x,Mortality_males_interpolated$y)
```
Health outcomes included in leisure time meta-analysis: all-cause mortality, cardiovascular disease, stroke, coronary heart disease, total cancer, colon, lung, endometrial, and breast cancer.

>>>>

```{r, echo=TRUE}
##I used spline function as the rates are not always monotonic.

##Loop to generate interpolated values for all cause mortality and all-cause years lived with disability.

i_sex <- c("male", "female")
i_measure <- c("deaths", "ylds (years lived with disability)")

for(sex in i_sex) {
  for (measure in i_measure) {

data <- filter(GBDGL, measure == "ylds (years lived with disability)", sex == "female", cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate)

x=data$age_cat
y=log(data$one_rate)

interpolated<- as.data.frame(spline(x, y, n = 5 *length (x), xmin = min(x-2), xmax = max(x + 2)))
interpolated$y <- exp(y)
plot(x,y)

  }
}

##Test here to generate all 4 data frames simultaneously.

i_sex <- c("male", "female")
i_measure <- c("deaths", "ylds (years lived with disability)")

for(sex in i_sex) {
  for (measure in i_measure) {

    data <- filter(GBDGL, measure == "ylds (years lived with disability)", sex == "female", cause == "all       causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate)
    assign(paste(i_sex, i_measure, "interpolated_data", sep = " "), data)
x=data$age_cat
y=log(data$one_rate)

interpolated <- as.data.frame(spline(x, y, n = 5 *length (x), xmin = min(x-2), xmax = max(x + 2)))
interpolated$y <- exp(y)
assign(paste(i_sex, i_measure, "interpolated", sep = " "), interpolated)
plot(x,y)

  }
}

```
Health outcomes included in leisure time meta-analysis: all-cause mortality, cardiovascular disease, stroke, coronary heart disease, total cancer, colon, lung, endometrial, and breast cancer.
